\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
redo first recruitment subsection

\subsection{Recruitment}
{\color {red}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

We recruited users from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}. 
The recruitment posting linked an online survey that collected their demographics, technical expertise, and familiarity with Tor.

Of our 16 participants, 53.3\% were male. 
Ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 
93.3\% of our participants had at least
a college education.
4 had used Tor before;
5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it. 
We distributed participants so that each experimental condition had at least one person who has never heard of Tor, at least one person who has only heard of Tor, and one person who has previously used Tor. The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.
}

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics. We pre-screened~\cite{screening} to have diversity of gender, age, technical expertise, and self-reported familiarity with Tor. The complete pre-screening survey can be found in Appendix~\ref{qualitative-prescreening}.

We recruited 16 participants for the test and distributed them evenly across environments:  5~in E1, 5~in E2, and 6~in E3. Of our 16 participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had at least a college education. 4 had used Tor before; 5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it. Although there is variation in gender, age, technical expertise in each experimental condition, we ensured each condition had a participant who has not heard of Tor, a participant who has heard of Tor, and a participant who has previously used Tor.
